---
title: "DataAnalysis_Ver2"
author: "Melissa"
date: "2023-06-12"
output: word_document
editor_options: 
  chunk_output_type: console
---
```{r package, include=FALSE}
library(readr)
library(agricolae)
library(ggplot2)
library(tidyverse)
library(cowplot)
library(GGally)
library(ggpattern)
library(leaps)
library(Hmisc)
library(corrplot)
library(lmtest)
flattenCorrMatrix <- function(cormat, pmat) {
  ut <- upper.tri(cormat)
  data.frame(
    row = rownames(cormat)[row(cormat)[ut]],
    column = rownames(cormat)[col(cormat)[ut]],
    cor  =(cormat)[ut],
    p = pmat[ut]
    )
}
```



```{r Dataset, include=FALSE}
setwd("C:/Users/melis/OneDrive - Universiti Putra Malaysia/Documents/GitHub/23_JRL_towardsagroecology")



Data <- read_csv("SALSADataset.csv")%>%
  select(-Direction)%>%
  na.omit()

colnames(Data)

Data$Year_Stability=as.factor(Data$Year_Stability)
Data$Year_CN=as.factor(Data$Year_CN)
Data$Year_Bulk=as.factor(Data$Year_CN)
Data$Block=as.factor(Data$Block)
Data$Year_covercrop=as.factor(Data$Year_covercrop)
Data$Plot=as.factor(Data$Plot)
Data$Depth=as.factor(Data$Depth)
Data$Treatment=as.factor(Data$Treatment)

str(Data)

```

```{r soilpropeties, echo=FALSE}
Stone_ratio= aov(`Stone:soil`~ Block , data=Data)
anova(Stone_ratio)
LSD_Stone_ratio= LSD.test(Stone_ratio, "Block")
LSD_Stone_ratio

SoilTX= aov(`DG_soilTx`~ Block, data=Data)
anova(SoilTX)
LSD_SoilTX= LSD.test(SoilTX, "Block")
LSD_SoilTX
```
 

## Stability Anova Test in 2019 and 2023

In this anova test, we will test the effect of treatment,block&plot(location) and year on soil stability. 

```{r Stability, echo=FALSE}
Stb=Data%>% 
  select (Treatment,Block,Plot,Rep,Year_Stability,Stability)%>%
  arrange(Year_Stability, Treatment)%>%
  na.omit()

Str_Stb= aov(Stability~Treatment+Year_Stability+Treatment*Year_Stability+Block, data=Stb)
anova(Str_Stb)

#Based on Anova, the plot did not affect the soil stability. 

#LSD Year
Str_Stb_Year= LSD.test(Str_Stb,"Year_Stability")
Str_Stb_Year

SigLetter_Year = Str_Stb_Year$groups%>%
  group_by(rownames(Str_Stb_Year$groups)) %>%
  arrange(rownames(Str_Stb_Year$groups))

names(SigLetter_Year)[3] = "Year"

print(SigLetter_Year)

#LSD Treatment (Overall performance)
Str_Stb_Trt= LSD.test(Str_Stb,"Treatment")
SigLetter_Stb_Trt = Str_Stb_Trt$groups%>%
  group_by(rownames(Str_Stb_Trt$groups)) %>%
  arrange(groups)

names(SigLetter_Stb_Trt)[3] = "Treatment"
print(SigLetter_Stb_Trt)

#LSD Block (Overall performance)
Str_Stb_Block= LSD.test(Str_Stb,"Block")
SigLetter_Stb_Block = Str_Stb_Block$groups%>%
  group_by(rownames(Str_Stb_Block$groups)) %>%
  arrange(groups)

names(SigLetter_Stb_Block)[3] = "Block"
print(SigLetter_Stb_Block)

#LSD Interaction between Treatment and Year
LSD_Test_TrtStb= LSD.test(Str_Stb, c("Treatment", "Year_Stability"))


SigLetter_TrtStb = LSD_Test_TrtStb$groups  %>%
  group_by(rownames(LSD_Test_TrtStb$groups)) %>%
  arrange(rownames(LSD_Test_TrtStb$groups))
names(SigLetter_TrtStb)[3] = "Interaction between Treatment and Year"
print(SigLetter_TrtStb)

Valuemax_TrtStb=Stb%>%
  group_by(Treatment,Year_Stability)%>%
  summarise(max_value=max(Stability))
  


ggplot(Data, aes(x=Treatment, y=Stability,fill=Year_Stability))+ geom_boxplot()+geom_text(data=Valuemax_TrtStb, aes(x=Treatment, y=0.1+max_value, label=SigLetter_TrtStb$groups),position = position_dodge(width = 0.9),vjust = -(0.5))+ ggtitle("Soil Stability in 2019 and 2023: \n The interaction between treatment and year")+theme(plot.title = element_text(hjust = 0.5),legend.position="bottom")
```


## Bulk Density in 2020 and 2023

```{r bulkdensity, echo=FALSE}
Bulk=Data%>% 
  select (Treatment,Block,Plot,Rep,Year_Bulk,Bulk_Density, Depth)%>%
  arrange(Year_Bulk, Treatment)%>%
  na.omit()

Ano_Bulk= aov(Bulk_Density~Treatment+Year_Bulk+Depth+Block+Treatment*Depth*Year_Bulk, data=Data)
anova(Ano_Bulk)


Bulk_Year= LSD.test(Ano_Bulk,"Year_Bulk")
Bulk_Year


Bulk_Trt= LSD.test(Ano_Bulk,"Treatment")
Bulk_Trt
Bulk_Block= LSD.test(Ano_Bulk,"Block")
Bulk_Block
Bulk_Depth = LSD.test(Ano_Bulk,"Depth")
Bulk_Depth 


### Interaction between treatment & Year 
LSD_Test_TrtYear= LSD.test(Ano_Bulk, c("Treatment", "Year_Bulk"))

SigLetter_TrtYear = LSD_Test_TrtYear$groups  %>%
  group_by(rownames(LSD_Test_TrtYear$groups)) %>%
  arrange(groups)

names(SigLetter_TrtYear)[3] = "Interaction between Treatment and year"

SigLetter_TrtYear= SigLetter_TrtYear%>%
  select(`Interaction between Treatment and year`, Bulk_Density, groups)
print(SigLetter_TrtYear)


### Interaction between treatment and depth
LSD_Test_TrtDepth= LSD.test(Ano_Bulk, c("Treatment", "Depth"))

SigLetter_TrtDepth = LSD_Test_TrtDepth$groups  %>%
  group_by(rownames(LSD_Test_TrtDepth$groups)) %>%
  arrange(groups)

names(SigLetter_TrtDepth)[3] = "Interaction between Treatment and depth"

SigLetter_TrtDepth= SigLetter_TrtDepth%>%
  select(`Interaction between Treatment and depth`, Bulk_Density, groups)

print(SigLetter_TrtDepth)

###Interaction between depth and year

### Interaction between Treatment,depth and year
LSD_Test_DepthYear= LSD.test(Ano_Bulk, c( "Depth", "Year_Bulk"))

SigLetter_DepthYear = LSD_Test_DepthYear$groups  %>%
  group_by(rownames(LSD_Test_DepthYear$groups)) %>%
  arrange(groups)

names(SigLetter_DepthYear)[3] = "Interaction between depth and year"

SigLetter_DepthYear= SigLetter_DepthYear%>%
  select(`Interaction between depth and year`, Bulk_Density, groups)
print(SigLetter_DepthYear)

### Interaction between Treatment,depth and year
LSD_Test_TrtDepthYear= LSD.test(Ano_Bulk, c("Treatment", "Depth", "Year_Bulk"))

SigLetter_TrtDepthYear = LSD_Test_TrtDepthYear$groups  %>%
  group_by(rownames(LSD_Test_TrtDepthYear$groups)) %>%
  arrange(groups)

names(SigLetter_TrtDepthYear)[3] = "Interaction between Treatment,depth and year"

SigLetter_TrtDepthYear= SigLetter_TrtDepthYear%>%
  select(`Interaction between Treatment,depth and year`, Bulk_Density, groups)
print(SigLetter_TrtDepthYear)
```


## Corelation Test

```{r correlation, eval=FALSE, include=FALSE}
X= Data %>% 
 select(11:29)

res2 <- rcorr(as.matrix(X))
#extarct r &p
correlatio_r = res2$r
correlation_p = res2$P

Corrlation_test1=flattenCorrMatrix(res2$r, res2$P)%>%
  filter(p<=0.05,cor<=-0.5)
Corrlation_test2=flattenCorrMatrix(res2$r, res2$P)%>%
  filter(p<=0.05,cor>=0.5)

#Select p<=0.05,cor>=0.5 or cor<=-0.5
Correlation=rbind(Corrlation_test1,Corrlation_test2)%>%
  select(-p)%>%
  arrange(cor)%>%
  mutate(`P-value<0.05`= "significant")

write.csv(Correlation,"C:/Users/melis/OneDrive - Universiti Putra Malaysia/Documents/GitHub/23_JRL_towardsagroecology/Correlation.csv",row.names=FALSE)


```

##Soil Stability Modelling. 

```{r StabilityModelling, echo=FALSE}

modelling=Data%>% 
  select(-Variety,-Year_CN)%>%
  na.omit()%>%
  group_by(Treatment,Block,Year_Stability,Depth)%>%
  summarise(Stability= mean(Stability),bulk=mean(Bulk_Density),TotalOM=mean(TotalOM),TotalN=mean(TotalN),CN= mean(CN),Cmin=mean(Cmin),`Cmin%`=mean(`Cmin%`), NH4=mean(NH4), NO3= mean(NO3), Nmin_Drysoil=mean(Nmin),`Nmin%`=mean(`Nmin%`), humidity=mean(Humidity), F_Mechanical=mean(`F_Mechanical actions`), soiltx=mean(DG_soilTx),`Stone:soil`=mean(`Stone:soil`) )        

            
modelling$Year_Stability=as.factor(modelling$Year_Stability)

Stb_1=lm(Stability~ Treatment+ TotalOM + Year_Stability +TotalN+CN+Cmin+`Cmin%`+ F_Mechanical+soiltx+`Stone:soil`, data=modelling)

AIC_Stb_1=step(Stb_1,direction="both")

Stb_2=lm(Stability ~ Treatment + Year_Stability + Cmin + `Cmin%`, data=modelling)
drop1(Stb_2,.~.,test="F")

Stb_3=lm(Stability ~ Treatment + Year_Stability + `Cmin%`, data=modelling)
drop1(Stb_3,.~.,test="F")

Stb_4=lm(Stability ~ Treatment + Year_Stability, data=modelling)
drop1(Stb_4,.~.,test="F")

summary(Stb_4)

```



**Model Assumption Check**

```{r normality, echo=FALSE, message=FALSE, warning=FALSE}
modelling$res.Stb_4=Stb_4 $residuals 
shapiro.test(modelling$res.Stb_4)
```
*It is normal*

2. Homoscedasticity Test

```{r Homoscedasticity, echo=FALSE, message=FALSE, warning=FALSE}
bptest(Stb_4)
```
It is homoscedasticity. 


##Stability Modelling Test 2. 

```{r Bulk_density, echo=FALSE}

colnames(modelling)

Bulk_model=Data%>% 
  select(-Variety,-Year_CN,-Year_Stability)%>%
  na.omit()%>%
  group_by(Treatment,Block,Year_Bulk,Depth)%>%
  summarise(Stability= mean(Stability),bulk=mean(Bulk_Density),TotalOM=mean(TotalOM),TotalN=mean(TotalN),CN= mean(CN),Cmin=mean(Cmin),`Cmin%`=mean(`Cmin%`), NH4=mean(NH4), NO3= mean(NO3), Nmin_Drysoil=mean(Nmin),`Nmin%`=mean(`Nmin%`), humidity=mean(Humidity), F_Mechanical=mean(`F_Mechanical actions`), soiltx=mean(DG_soilTx),`Stone:soil`=mean(`Stone:soil`) )        

Bulk.1=lm(bulk~ Treatment+ TotalOM + Year_Bulk + Depth+ +TotalN+CN+Cmin+`Cmin%`+NO3+NH4+Nmin_Drysoil+`Nmin%`+humidity+F_Mechanical+soiltx+`Stone:soil`, data=Bulk_model)

AIC_Bulk.1=step(Bulk.1,direction="both")

Bulk.2=lm(bulk ~ `Nmin%` + humidity + soiltx, data=Bulk_model)
drop1(Bulk.2,.~.,test="F")

summary(Bulk.2)


Bulk_model$res.Bulk.2=Bulk.2 $residuals 
shapiro.test(Bulk_model$res.Bulk.2)

ggplot(Bulk_model, aes(sample = res.Bulk.2)) +
stat_qq() +
stat_qq_line()+
labs(title = "Normal Q-Q Plot of Stb_3.2")

bptest(Bulk.2)

```

Stb_2=lm(Stability ~ Treatment + TotalOM + Year_Stability + TotalN + CN + Cmin + `Cmin%` + NO3 + NH4 + Nmin_Drysoil + `Nmin%` + humidity, data=modelling)


##TotalOM

```{r TotalOM}
colnames(Data)

Total_OM= lm(TotalOM~Treatment+Block+Year_CN+Treatment*Year_CN, data=Data)
anova(Total_OM)

#LSD Year
TotalOM_Year= LSD.test(Total_OM,"Year_CN")
TotalOM_Year


#LSD Treatment (Overall performance)
TotalOM_Trt= LSD.test(Total_OM,"Treatment")
TotalOM_Trt


#LSD Interaction between Treatment and Year
LSD_TotalOM_TrtYear= LSD.test(Total_OM, c("Treatment", "Year_CN"))
LSD_TotalOM_TrtYear

SigLetter_TotalOM_TrtYear = LSD_TotalOM_TrtYear$groups  %>%
  group_by(rownames(LSD_TotalOM_TrtYear$groups)) %>%
  arrange(rownames(LSD_TotalOM_TrtYear$groups))
names(SigLetter_TotalOM_TrtYear)[3] = "Total OM: Interaction between Treatment and Year"
print(SigLetter_TotalOM_TrtYear)


Valuemax_TotalOM_TrtStb=Data%>%
  group_by(Treatment,Year_CN)%>%
  summarise(max_value=max(TotalOM))

p1=ggplot(Data, aes(x=Treatment, y=TotalOM,fill=Year_CN))+ geom_boxplot()+geom_text(data=Valuemax_TotalOM_TrtStb, aes(x=Treatment, y=0.1+max_value, label=SigLetter_TotalOM_TrtYear$groups),position = position_dodge(width = 0.9),vjust = -(0.5))+theme(legend.position="bottom")
```

##TotalN

```{r TotalN}
colnames(Data)

TotalN= lm(TotalN~Treatment+Block+Year_CN+Treatment*Year_CN, data=Data)
anova(TotalN)

#LSD Year
TotalN_Year= LSD.test(TotalN,"Year_CN")
TotalN_Year


#LSD Treatment (Overall performance)
TotalN_Trt= LSD.test(TotalN,"Treatment")
TotalN_Trt


#LSD Interaction between Treatment and Year
LSD_TotalN_TrtYear= LSD.test(TotalN, c("Treatment", "Year_CN"))
LSD_TotalN_TrtYear

SigLetter_TotalN_TrtYear = LSD_TotalN_TrtYear$groups  %>%
  group_by(rownames(LSD_TotalN_TrtYear$groups)) %>%
  arrange(rownames(LSD_TotalN_TrtYear$groups))
names(SigLetter_TotalN_TrtYear)[3] = "Total N: Interaction between Treatment and Year"
print(SigLetter_TotalN_TrtYear)

Valuemax_TotalN_TrtStb=Data%>%
  group_by(Treatment,Year_CN)%>%
  summarise(max_value=max(TotalN))

p2=ggplot(Data, aes(x=Treatment, y=TotalN,fill=Year_CN))+ geom_boxplot()+geom_text(data=Valuemax_TotalN_TrtStb, aes(x=Treatment, y=0.1+max_value, label=SigLetter_TotalN_TrtYear$groups),position = position_dodge(width = 0.9),vjust = -(0.5))+theme(legend.position="bottom")
```

##CN Ratio

```{r CN}
colnames(Data)

CN= lm(CN~Treatment+Block+Year_CN+Treatment*Year_CN, data=Data)
anova(CN)

#LSD Year
CN_Year= LSD.test(CN,"Year_CN")
CN_Year


#LSD Treatment (Overall performance)
CN_Trt= LSD.test(CN,"Treatment")
CN_Trt


#LSD Interaction between Treatment and Year
LSD_CN_TrtYear= LSD.test(CN, c("Treatment", "Year_CN"))
LSD_CN_TrtYear

SigLetter_CN_TrtYear = LSD_CN_TrtYear$groups  %>%
  group_by(rownames(LSD_CN_TrtYear$groups)) %>%
  arrange(rownames(LSD_CN_TrtYear$groups))
names(SigLetter_CN_TrtYear)[3] = "CN: Interaction between Treatment and Year"
print(SigLetter_CN_TrtYear)

Valuemax_CN_TrtStb=Data%>%
  group_by(Treatment,Year_CN)%>%
  summarise(max_value=max(CN))

p3=ggplot(Data, aes(x=Treatment, y=CN,fill=Year_CN))+ geom_boxplot()+geom_text(data=Valuemax_CN_TrtStb, aes(x=Treatment, y=0.1+max_value, label=SigLetter_CN_TrtYear$groups),position = position_dodge(width = 0.9),vjust = -(0.5))+theme(legend.position="bottom")
```

## Cmin

```{r Cmin}
colnames(Data)

Cmin= lm(Cmin~Treatment+Block+Year_CN+Treatment*Year_CN, data=Data)
anova(Cmin)

#LSD Year
Cmin_Year= LSD.test(Cmin,"Year_CN")
Cmin_Year


#LSD Treatment (Overall performance)
Cmin_Trt= LSD.test(Cmin,"Treatment")
Cmin_Trt


#LSD Interaction between Treatment and Year
LSD_Cmin_TrtYear= LSD.test(Cmin, c("Treatment", "Year_CN"))
LSD_Cmin_TrtYear

SigLetter_Cmin_TrtYear = LSD_Cmin_TrtYear$groups  %>%
  group_by(rownames(LSD_Cmin_TrtYear$groups)) %>%
  arrange(rownames(LSD_Cmin_TrtYear$groups))
names(SigLetter_Cmin_TrtYear)[3] = "Cmin: Interaction between Treatment and Year"
print(SigLetter_Cmin_TrtYear)

Valuemax_Cmin_TrtStb=Data%>%
  group_by(Treatment,Year_CN)%>%
  summarise(max_value=max(Cmin))

p4=ggplot(Data, aes(x=Treatment, y=Cmin,fill=Year_CN))+ geom_boxplot()+geom_text(data=Valuemax_Cmin_TrtStb, aes(x=Treatment, y=0.1+max_value, label=SigLetter_Cmin_TrtYear$groups),position = position_dodge(width = 0.9),vjust = -(0.5))+theme(legend.position="bottom")
```

##Cmin%

```{r Cminpgc}
Cminpcg= lm(`Cmin%`~Treatment+Block+Year_CN+Treatment*Year_CN, data=Data)
anova(Cminpcg)

#LSD Year
Cminpcg_Year= LSD.test(Cminpcg,"Year_CN")
Cminpcg_Year


#LSD Treatment (Overall performance)
Cminpcg_Trt= LSD.test(Cminpcg,"Treatment")
Cminpcg_Trt


#LSD Interaction between Treatment and Year
LSD_Cminpcg_TrtYear= LSD.test(Cminpcg, c("Treatment", "Year_CN"))
LSD_Cminpcg_TrtYear

SigLetter_Cminpcg_TrtYear = LSD_Cminpcg_TrtYear$groups  %>%
  group_by(rownames(LSD_Cminpcg_TrtYear$groups)) %>%
  arrange(rownames(LSD_Cminpcg_TrtYear$groups))
names(SigLetter_Cminpcg_TrtYear)[3] = "Cmin%: Interaction between Treatment and Year"
print(SigLetter_Cminpcg_TrtYear)

Valuemax_Cminpcg_TrtStb=Data%>%
  group_by(Treatment,Year_CN)%>%
  summarise(max_value=max(`Cmin%`))

p5=ggplot(Data, aes(x=Treatment, y=`Cmin%`,fill=Year_CN))+ geom_boxplot()+geom_text(data=Valuemax_Cminpcg_TrtStb, aes(x=Treatment, y=0.1+max_value, label=SigLetter_Cminpcg_TrtYear$groups),position = position_dodge(width = 0.9),vjust = -(0.5))+theme(legend.position="bottom")
```




##NO3
```{r NO3}

NO3= lm(NO3~Treatment+Block+Year_CN+Treatment*Year_CN, data=Data)
anova(NO3)

#LSD Year
NO3_Year= LSD.test(NO3,"Year_CN")
NO3_Year


#LSD Treatment (Overall performance)
NO3_Trt= LSD.test(NO3,"Treatment")
NO3_Trt


#LSD Interaction between Treatment and Year
LSD_NO3_TrtYear= LSD.test(NO3, c("Treatment", "Year_CN"))
LSD_NO3_TrtYear

SigLetter_NO3_TrtYear = LSD_NO3_TrtYear$groups  %>%
  group_by(rownames(LSD_NO3_TrtYear$groups)) %>%
  arrange(rownames(LSD_NO3_TrtYear$groups))
names(SigLetter_NO3_TrtYear)[3] = "NO3: Interaction between Treatment and Year"
print(SigLetter_NO3_TrtYear)

Valuemax_NO3_TrtStb=Data%>%
  group_by(Treatment,Year_CN)%>%
  summarise(max_value=max(`NO3`))

p6=ggplot(Data, aes(x=Treatment, y=`NO3`,fill=Year_CN))+ geom_boxplot()+geom_text(data=Valuemax_NO3_TrtStb, aes(x=Treatment, y=0.1+max_value, label=SigLetter_NO3_TrtYear$groups),position = position_dodge(width = 0.9),vjust = -(0.5))+theme(legend.position="bottom")
```

##NH4
```{r NH4}
colnames(Data)

NH4= lm(NH4~Treatment+Block+Year_CN+Treatment*Year_CN, data=Data)
anova(NH4)

#LSD Year
NH4_Year= LSD.test(NH4,"Year_CN")
NH4_Year


#LSD Treatment (Overall performance)
NH4_Trt= LSD.test(NH4,"Treatment")
NH4_Trt


#LSD Interaction between Treatment and Year
LSD_NH4_TrtYear= LSD.test(NH4, c("Treatment", "Year_CN"))
LSD_NH4_TrtYear

SigLetter_NH4_TrtYear = LSD_NH4_TrtYear$groups  %>%
  group_by(rownames(LSD_NH4_TrtYear$groups)) %>%
  arrange(rownames(LSD_NH4_TrtYear$groups))
names(SigLetter_NH4_TrtYear)[3] = "NH4: Interaction between Treatment and Year"
print(SigLetter_NH4_TrtYear)

Valuemax_NH4_TrtStb=Data%>%
  group_by(Treatment,Year_CN)%>%
  summarise(max_value=max(NH4))

p7=ggplot(Data, aes(x=Treatment, y=NH4,fill=Year_CN))+ geom_boxplot()+geom_text(data=Valuemax_NO3_TrtStb, aes(x=Treatment, y=0.1+max_value, label=SigLetter_NH4_TrtYear$groups),position = position_dodge(width = 0.9),vjust = -(0.5))+theme(legend.position="bottom")
```

##Nmin
```{r Nmin}
colnames(Data)

Nmin= lm(Nmin~Treatment+Block+Year_CN+Treatment*Year_CN, data=Data)
anova(Nmin)

#LSD Year
Nmin_Year= LSD.test(Nmin,"Year_CN")
Nmin_Year


#LSD Treatment (Overall performance)
Nmin_Trt= LSD.test(Nmin,"Treatment")
Nmin_Trt


#LSD Interaction between Treatment and Year
LSD_Nmin_TrtYear= LSD.test(Nmin, c("Treatment", "Year_CN"))
LSD_Nmin_TrtYear

SigLetter_Nmin_TrtYear = LSD_Nmin_TrtYear$groups  %>%
  group_by(rownames(LSD_Nmin_TrtYear$groups)) %>%
  arrange(rownames(LSD_Nmin_TrtYear$groups))
names(SigLetter_Nmin_TrtYear)[3] = "Nmin: Interaction between Treatment and Year"
print(SigLetter_NH4_TrtYear)

Valuemax_Nmin_TrtStb=Data%>%
  group_by(Treatment,Year_CN)%>%
  summarise(max_value=max(Nmin))

p8=ggplot(Data, aes(x=Treatment, y=Nmin,fill=Year_CN))+ geom_boxplot()+geom_text(data=Valuemax_Nmin_TrtStb, aes(x=Treatment, y=0.1+max_value, label=SigLetter_Nmin_TrtYear$groups),position = position_dodge(width = 0.9),vjust = -(0.5))+theme(legend.position="bottom")
```

##Soil moisture
```{r moisture}
colnames(Data)

Humidity= lm(Humidity~Treatment+Block+Year_CN+Treatment*Year_CN, data=Data)
anova(Humidity)

#LSD Year
Humidity_Year= LSD.test(Humidity,"Year_CN")
Humidity_Year


#LSD Treatment (Overall performance)
Humidity_Trt= LSD.test(Humidity,"Treatment")
Humidity_Trt


#LSD Interaction between Treatment and Year
LSD_Humidity_TrtYear= LSD.test(Humidity, c("Treatment", "Year_CN"))
LSD_Humidity_TrtYear

SigLetter_Humidity_TrtYear = LSD_Humidity_TrtYear$groups  %>%
  group_by(rownames(LSD_Humidity_TrtYear$groups)) %>%
  arrange(rownames(LSD_Humidity_TrtYear$groups))
names(SigLetter_Humidity_TrtYear)[3] = "Humidity: Interaction between Treatment and Year"
print(SigLetter_NH4_TrtYear)

Valuemax_Humidity_TrtStb=Data%>%
  group_by(Treatment,Year_CN)%>%
  summarise(max_value=max(Humidity))

p9=ggplot(Data, aes(x=Treatment, y=Humidity,fill=Year_CN))+ geom_boxplot()+geom_text(data=Valuemax_Humidity_TrtStb, aes(x=Treatment, y=0.1+max_value, label=SigLetter_Humidity_TrtYear$groups),position = position_dodge(width = 0.9),vjust = -(0.5))+theme(legend.position="bottom")

```

##Nmin%

```{r Nminpcg}
Nminpcg= lm(`Nmin%`~Treatment+Block+Year_CN+Treatment*Year_CN, data=Data)
anova(Cminpcg)

#LSD Year
Nminpcg_Year= LSD.test(Cminpcg,"Year_CN")
Nminpcg_Year


#LSD Treatment (Overall performance)
Nminpcg_Trt= LSD.test(Cminpcg,"Treatment")
Nminpcg_Trt


#LSD Interaction between Treatment and Year
LSD_Nminpcg_TrtYear= LSD.test(Nminpcg, c("Treatment", "Year_CN"))
LSD_Nminpcg_TrtYear

SigLetter_Nminpcg_TrtYear = LSD_Nminpcg_TrtYear$groups  %>%
  group_by(rownames(LSD_Nminpcg_TrtYear$groups)) %>%
  arrange(rownames(LSD_Nminpcg_TrtYear$groups))
names(SigLetter_Nminpcg_TrtYear)[3] = "Cmin%: Interaction between Treatment and Year"
print(SigLetter_Nminpcg_TrtYear)

Valuemax_Nminpcg_TrtStb=Data%>%
  group_by(Treatment,Year_CN)%>%
  summarise(max_value=max(`Nmin%`))

p10=ggplot(Data, aes(x=Treatment, y=`Nmin%`,fill=Year_CN))+ geom_boxplot()+geom_text(data=Valuemax_Nminpcg_TrtStb, aes(x=Treatment, y=0.1+max_value, label=SigLetter_Nminpcg_TrtYear$groups),position = position_dodge(width = 0.9),vjust = -(0.5))+theme(legend.position="bottom")


plot_grid(
p1,p2,p3,
nrow = 1, ncol = 3)

plot_grid(
p4,p5,p6,
nrow = 1, ncol = 3)

plot_grid(
p7,p8,p10,p9,
nrow = 1, ncol = 4)
```

##Cover_DM_t_ha

```{r Cover_DM_t_ha}
colnames(Data)

Cover_DM_t_ha= lm(Cover_DM_t_ha~Treatment+Block+Year_covercrop+Treatment*Year_covercrop, data=Data)
anova(Cover_DM_t_ha)

#LSD Year
Cover_DM_t_ha_Year= LSD.test(Cover_DM_t_ha,"Year_covercrop")
Cover_DM_t_ha_Year


#LSD Treatment (Overall performance)
Cover_DM_t_ha_Trt= LSD.test(Cover_DM_t_ha,"Treatment")
Cover_DM_t_ha_Trt


#LSD Interaction between Treatment and Year
LSD_Cover_DM_t_ha_TrtYear= LSD.test(Cover_DM_t_ha, c("Treatment", "Year_covercrop"))
LSD_Cover_DM_t_ha_TrtYear

SigLetter_Cover_DM_t_ha_TrtYear = LSD_Cover_DM_t_ha_TrtYear$groups  %>%
  group_by(rownames(LSD_Cover_DM_t_ha_TrtYear$groups)) %>%
  arrange(rownames(LSD_Cover_DM_t_ha_TrtYear$groups))
names(SigLetter_Cover_DM_t_ha_TrtYear)[3] = "Cover_DM_t_ha: Interaction between Treatment and Year"
print(SigLetter_Cover_DM_t_ha_TrtYear)

Valuemax_Cover_DM_t_ha_TrtStb=Data%>%
  group_by(Treatment,Year_covercrop)%>%
  summarise(max_value=max(Cover_DM_t_ha))

p11= ggplot(Data, aes(x=Treatment, y=Cover_DM_t_ha,fill=Year_covercrop))+ geom_boxplot()+geom_text(data=Valuemax_Cover_DM_t_ha_TrtStb, aes(x=Treatment, y=0.1+max_value, label=SigLetter_Cover_DM_t_ha_TrtYear$groups),position = position_dodge(width = 0.9),vjust = -(0.5))+theme(legend.position="bottom")
```

##Cover_potRestit_N

```{r Cover_potRestit_N}
colnames(Data)

Cover_potRestit_N= lm(Cover_potRestit_N~Treatment+Block+Year_covercrop+Treatment*Year_covercrop, data=Data)
anova(Cover_potRestit_N)

#LSD Year
Cover_potRestit_N_Year= LSD.test(Cover_potRestit_N,"Year_covercrop")
Cover_potRestit_N_Year


#LSD Treatment (Overall performance)
Cover_potRestit_N_Trt= LSD.test(Cover_potRestit_N,"Treatment")
Cover_potRestit_N_Trt


#LSD Interaction between Treatment and Year
LSD_Cover_potRestit_N_TrtYear= LSD.test(Cover_potRestit_N, c("Treatment", "Year_covercrop"))
LSD_Cover_DM_t_ha_TrtYear

SigLetter_Cover_potRestit_N_TrtYear = LSD_Cover_potRestit_N_TrtYear$groups  %>%
  group_by(rownames(LSD_Cover_potRestit_N_TrtYear$groups)) %>%
  arrange(rownames(LSD_Cover_potRestit_N_TrtYear$groups))
names(SigLetter_Cover_potRestit_N_TrtYear)[3] = "Cover_potRestit_N: Interaction between Treatment and Year"
print(SigLetter_Cover_potRestit_N_TrtYear)

Valuemax_Cover_potRestit_N_TrtStb=Data%>%
  group_by(Treatment,Year_covercrop)%>%
  summarise(max_value=max(Cover_potRestit_N))

p12=ggplot(Data, aes(x=Treatment, y=Cover_potRestit_N,fill=Year_covercrop))+ geom_boxplot()+geom_text(data=Valuemax_Cover_potRestit_N_TrtStb, aes(x=Treatment, y=0.1+max_value, label=SigLetter_Cover_potRestit_N_TrtYear$groups),position = position_dodge(width = 0.9),vjust = -(0.5))+theme(legend.position="bottom")
```

##Cover_mesRestit_N

```{r Cover_mesRestit_N}
colnames(Data)

Cover_mesRestit_N= lm(Cover_mesRestit_N~Treatment+Block+Year_covercrop+Treatment*Year_covercrop, data=Data)
anova(Cover_mesRestit_N)

#LSD Year
Cover_mesRestit_N_Year= LSD.test(Cover_mesRestit_N,"Year_covercrop")
Cover_mesRestit_N_Year


#LSD Treatment (Overall performance)
Cover_mesRestit_N_Trt= LSD.test(Cover_mesRestit_N,"Treatment")
Cover_mesRestit_N_Trt


#LSD Interaction between Treatment and Year
LSD_Cover_mesRestit_N_TrtYear= LSD.test(Cover_mesRestit_N, c("Treatment", "Year_covercrop"))
LSD_Cover_DM_t_ha_TrtYear

SigLetter_Cover_mesRestit_N_TrtYear = LSD_Cover_mesRestit_N_TrtYear$groups  %>%
  group_by(rownames(LSD_Cover_mesRestit_N_TrtYear$groups)) %>%
  arrange(rownames(LSD_Cover_mesRestit_N_TrtYear$groups))
names(SigLetter_Cover_mesRestit_N_TrtYear)[3] = "Cover_mesRestit_N: Interaction between Treatment and Year"
print(SigLetter_Cover_mesRestit_N_TrtYear)

Valuemax_Cover_mesRestit_N_TrtStb=Data%>%
  group_by(Treatment,Year_covercrop)%>%
  summarise(max_value=max(Cover_mesRestit_N))

p13=ggplot(Data, aes(x=Treatment, y=Cover_mesRestit_N,fill=Year_covercrop))+ geom_boxplot()+geom_text(data=Valuemax_Cover_mesRestit_N_TrtStb, aes(x=Treatment, y=0.1+max_value, label=SigLetter_Cover_mesRestit_N_TrtYear$groups),position = position_dodge(width = 0.9),vjust = -(0.5))+theme(legend.position="bottom")
```

##Cover_mesRestit_N

```{r Cover_mesRestit_N}
colnames(Data)

Cover_mesRestit_C= lm(Cover_mesRestit_C~Treatment+Block+Year_covercrop+Treatment*Year_covercrop, data=Data)
anova(Cover_mesRestit_C)

#LSD Year
Cover_mesRestit_C_Year= LSD.test(Cover_mesRestit_C,"Year_covercrop")
Cover_mesRestit_C_Year


#LSD Treatment (Overall performance)
Cover_mesRestit_C_Trt= LSD.test(Cover_mesRestit_C,"Treatment")
Cover_mesRestit_C_Trt


#LSD Interaction between Treatment and Year
LSD_Cover_mesRestit_C_TrtYear= LSD.test(Cover_mesRestit_C, c("Treatment", "Year_covercrop"))
LSD_Cover_DM_t_ha_TrtYear

SigLetter_Cover_mesRestit_C_TrtYear = LSD_Cover_mesRestit_C_TrtYear$groups  %>%
  group_by(rownames(LSD_Cover_mesRestit_C_TrtYear$groups)) %>%
  arrange(rownames(LSD_Cover_mesRestit_C_TrtYear$groups))
names(SigLetter_Cover_mesRestit_C_TrtYear)[3] = "Cover_mesRestit_C: Interaction between Treatment and Year"
print(SigLetter_Cover_mesRestit_C_TrtYear)

Valuemax_Cover_mesRestit_C_TrtStb=Data%>%
  group_by(Treatment,Year_covercrop)%>%
  summarise(max_value=max(Cover_mesRestit_C))

p14=ggplot(Data, aes(x=Treatment, y=Cover_mesRestit_C,fill=Year_covercrop))+ geom_boxplot()+geom_text(data=Valuemax_Cover_mesRestit_C_TrtStb, aes(x=Treatment, y=0.1+max_value, label=SigLetter_Cover_mesRestit_C_TrtYear$groups),position = position_dodge(width = 0.9),vjust = -(0.5))+theme(legend.position="bottom")

plot_grid(
p11,p12,p13,p14,
nrow = 1, ncol = 4)

```
