---
title: "SALSA_JRL Data Analysis Final Version "
output: html_document
date: "2023-06-25"
editor_options: 
  chunk_output_type: console
---
```{r package, include=FALSE}
library(readr)
library(agricolae)
library(ggplot2)
library(tidyverse)
library(cowplot)
library(GGally)
library(ggpattern)
library(leaps)
library(Hmisc)
library(corrplot)
library(lmtest)
library(tinytex)
library(equatiomatic)
library(ggpubr)
flattenCorrMatrix <- function(cormat, pmat) {
  ut <- upper.tri(cormat)
  data.frame(
    row = rownames(cormat)[row(cormat)[ut]],
    column = rownames(cormat)[col(cormat)[ut]],
    cor  =(cormat)[ut],
    p = pmat[ut]
    )
}
```

```{r workingdirectory, include=FALSE}
setwd("C:/Users/melis/OneDrive - Universiti Putra Malaysia/Documents/GitHub/23_JRL_towardsagroecology")
```

# Block Effect 

Note:
- stone:soil ratio collected in 2020 and 2023
These soil physical properties cant be alter in short period. 
  obs stone:soil: 3 block x 3 trt x 3 plots X 2 years=  54 
  
- Soil texture collected in 2019 
  obs stone:soil: 3 block x 3 trt x 3 plots =  27


```{r datainput, echo=FALSE}

Stability <- read_csv("Stability.csv", col_types = cols(Year_Covercrop = col_factor(levels = c()), 
    Year_Stability = col_factor(levels = c()), 
    Year_CN = col_factor(levels = c()), Trt = col_factor(levels = c()), 
    Block = col_factor(levels = c()), Stability = col_number(), 
    TotalOM = col_number(), soiltx = col_factor(levels = c())))
```

## Stone soil ratio in 2019

```{r stone_2019, echo=FALSE}

Stone_19=which(Stability$Year_Stability=="2019")

Stone_19=Stability[Stone_19,]

Stone_19.1= lm(Stone_soil~Trt+Block, data=Stone_19)
anova(Stone_19.1)
LSD_Stone_19.1=LSD.test(Stone_19.1,"Block")
LSD_Stone_19.1

SigLetter_LSD_Stone_19.1 = LSD_Stone_19.1$groups  %>%
  group_by(rownames(LSD_Stone_19.1$groups)) %>%
  arrange(rownames(LSD_Stone_19.1$groups))

Valuemax_LSD_Stone_19.1=Stone_19 %>%
  group_by(Block)%>%
  summarise(max_value=mean(Stone_soil))


S1=ggplot(Stone_19, aes(x=Block, Stone_soil))+ geom_boxplot()+geom_text(data=Valuemax_LSD_Stone_19.1, aes(x=Block, y=0.1+max_value, label=SigLetter_LSD_Stone_19.1$groups),position = position_dodge(width = 0.9),vjust = -(0.5))+theme(plot.title = element_text(hjust = 0.5),legend.position="bottom")+ ylab("Stone:soil ratio \n 2019")+ xlab("Block")+ theme(
axis.title.x = element_text(size=14),
axis.title.y = element_text(size=14)
)
```


## Stone soil ratio in 2023


```{r stone_2023, echo=FALSE}
Stone_23=which(Stability$Year_Stability=="2023")

Stone_23=Stability[Stone_23,]


Stone_23.1= lm(Stone_soil~Trt+Block, data=Stone_23)
anova(Stone_23.1)
LSD_Stone_23.1=LSD.test(Stone_23.1,"Block")
LSD_Stone_23.1

SigLetter_LSD_Stone_23.1 = LSD_Stone_23.1$groups  %>%
  group_by(rownames(LSD_Stone_23.1$groups)) %>%
  arrange(rownames(LSD_Stone_23.1$groups))

Valuemax_LSD_Stone_23.1=Stone_23 %>%
  group_by(Block)%>%
  summarise(max_value=mean(Stone_soil))


S2=ggplot(Stone_23, aes(x=Block, Stone_soil))+ geom_boxplot()+geom_text(data=Valuemax_LSD_Stone_23.1, aes(x=Block, y=0.1+max_value, label=SigLetter_LSD_Stone_23.1$groups),position = position_dodge(width = 0.9),vjust = -(0.5))+theme(plot.title = element_text(hjust =0.5),legend.position="bottom")+ ylab("Stone:soil ratio \n 2023")+ xlab("Block")+ theme(
axis.title.x = element_text(size=14),
axis.title.y = element_text(size=14)
)


LSD_Stone_23.2=LSD.test(Stone_23.1,"Trt")
LSD_Stone_23.2

SigLetter_LSD_Stone_23.2 = LSD_Stone_23.2$groups  %>%
  group_by(rownames(LSD_Stone_23.2$groups)) %>%
  arrange(rownames(LSD_Stone_23.2$groups))

Valuemax_LSD_Stone_23.2=Stone_23 %>%
  group_by(Trt)%>%
  summarise(max_value=mean(Stone_soil))


S3=ggplot(Stone_23, aes(x=Trt, Stone_soil))+ geom_boxplot()+geom_text(data=Valuemax_LSD_Stone_23.2, aes(x=Trt, y=0.1+max_value, label=SigLetter_LSD_Stone_23.2$groups),position = position_dodge(width = 0.9),vjust = -(0.5))+theme(plot.title = element_text(hjust =0.5),legend.position="bottom")+ ylab("Stone:soil ratio \n 2023")+ xlab("Treatment")+ theme(
axis.title.x = element_text(size=14),
axis.title.y = element_text(size=14)
)
```


## Soil texture in 2019


```{r tx_2019, echo=FALSE}

list_tx=which(Stability$Year_Stability=="2019"&Stability$Plot=="1")

tx=Stability[list_tx,]

dgtx= lm(dgtx~Block+Trt, data=tx)
anova(dgtx)


S4=ggplot(tx, aes(x=Block, y=dgtx))+ geom_boxplot()+ ylab("Geometric mean of \n particle size distribution \n  (dg)\n 2019")+ xlab("Block")+ theme(
axis.title.x = element_text(size=14),
axis.title.y = element_text(size=14)
)


plot_grid(
S4,S1,S2,S3,
nrow = 2,ncol=2)


```



# Soil stability in 2019& 2023
- obs soil stability in 2019: 3 block x 3 trt x 3 plots=27 
- obs soil stability in 2023: 3 block x 3 trt x 3 plots=27 

## Soil stability in 2019


```{r Stability_2019, echo=FALSE}
#focus in 2019
list_stb2019=which(Stability$Year_Stability=="2019")

stb2019=Stability[list_stb2019,]
stb.19= lm(Stability~Trt+Block, data=stb2019)
anova(stb.19)

lsd_stb.19=LSD.test(stb.19,"Trt")
lsd_stb.19
```


## Soil stability in 2023


```{r Stability_2023, echo=FALSE}
list_stb2023=which(Stability$Year_Stability=="2023")

stb2023=Stability[list_stb2023,]

stb.23= lm(Stability~Trt+Block, data=stb2023)
anova(stb.23)

lsd_stb.23=LSD.test(stb.23,"Trt")
lsd_stb.23
```


## Soil stability in 2019 2023


```{r Stability, echo=FALSE}
stb.1= lm(Stability~Trt+Block, data=Stability)
stb.2=lm(Stability~Trt+Block+Year_Stability, data=Stability)
stb.3=lm(Stability~Trt+Block+Year_Stability+Trt*Year_Stability, data=Stability)

anova(stb.3)

lsd_stb.inter=LSD.test(stb.3,c("Trt","Year_Stability"))
lsd_stb.inter

SigLetter_lsd_stb.inter = lsd_stb.inter$groups  %>%
  group_by(rownames(lsd_stb.inter$groups)) %>%
  arrange(rownames(lsd_stb.inter$groups))

Valuemax_lsd_stb.inter=Stability %>%
  group_by(Trt,Year_Stability)%>%
  summarise(max_value=mean(Stability))


ggplot(Stability, aes(x=Trt, y=Stability,fill=Year_Stability))+ geom_boxplot()+geom_text(data=Valuemax_lsd_stb.inter, aes(x=Trt, y=0.3+max_value, label=SigLetter_lsd_stb.inter$groups),position = position_dodge(width = 0.9),vjust = -(0.5))+theme(plot.title = element_text(hjust =0.5),legend.position="bottom")+ ylab("Soil Stability (MWD)")+ xlab("Treatment")
```


### The normal distribution of soil stability in 2019 and 2023
- obs soil stability in 2019 $ 2023: 3 block x 3 trt x 3 plots x 2 years=54


```{r stb distribution, echo=FALSE}


list_stb_t=which(Stability$Trt=="T_Viti")
stb_t=Stability[list_stb_t,]


list_stb_A=which(Stability$Trt=="A_Viti")
stb_A=Stability[list_stb_A,]


list_stb_D=which(Stability$Trt=="D_Viti")
stb_D=Stability[list_stb_D,]



d1=ggdensity(stb_t, x = "Stability", fill = "lightgray", title = "T_Viti") + ylab("Number of Data Points")+ xlab("Stability")+ ylim(0, 2.5)
d2=ggdensity(stb_A, x = "Stability", fill = "lightgray", title = "A_Viti") + ylab("Number of Data Points")+ xlab("Stability")+ ylim(0, 2.5)
d3=ggdensity(stb_D, x = "Stability", fill = "lightgray", title = "D_Viti") + ylab("Number of Data Points")+ xlab("Stability")+ ylim(0, 2.5)

plot_grid(
  d1,d2,d3,
  nrow=1,ncol=3
)

```



# Total Organic Matter in 2022
obs=3 trts x 3 blocks x 3 plots =27


```{r stb_Tom, echo=FALSE}
List.stb_tom=which(Stability$Year_Stability=="2023")

stb_tom=Stability[List.stb_tom,]


c1=ggscatter(stb_tom, x = "TotalOM", y = "Stability", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Total organic matter(%) \n in 2022", ylab = "Soil stability (MWD) \n in 2023")

c2=ggscatter(stb_tom, x = "CN", y = "Stability", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "C:N ratio in 2022", ylab = "Soil stability (MWD)\n in 2023")

plot_grid(
  c1,c2,
  nrow=1,ncol=2
)

tom1=lm(TotalOM~Trt+Block, data=stb_tom)
anova(tom1)

lsd_OM=LSD.test(tom1,"Trt")
lsd_OM

SigLetter_OM = lsd_OM$groups  %>%
  group_by(rownames(lsd_OM$groups)) %>%
  arrange(rownames(lsd_OM$groups))

Valuemax_lsd_OM=stb_tom %>%
  group_by(Trt)%>%
  summarise(max_value=mean(TotalOM))
lsd_OM=LSD.test(tom1,"Trt")


lsd_OM_b=LSD.test(tom1,"Block")


ggplot(stb_tom, aes(x=Trt, y=TotalOM))+ geom_boxplot()+geom_text(data=Valuemax_lsd_OM, aes(x=Trt, y=0.1+max_value, label=SigLetter_OM$groups),position = position_dodge(width = 0.9),vjust = -(0.5))+theme(plot.title = element_text(hjust = 0.5),legend.position="bottom")+ ylab("Total Organic Matter (%)\n 2022")+ xlab("Treatment")
```

# CN Ratio in 2022
obs=3 trts x 3 blocks x 3 plots =27


```{r CN}
CN=lm(CN~Trt+Block, data=stb_tom)
anova(CN)

lsd_CN=LSD.test(CN,"Trt")
lsd_CN

SigLetter_CN= lsd_CN$groups  %>%
  group_by(rownames(lsd_CN$groups)) %>%
  arrange(rownames(lsd_CN$groups))

Valuemax_lsd_CN=stb_tom %>%
  group_by(Trt)%>%
  summarise(max_value=mean(CN))


ggplot(stb_tom, aes(x=Trt, y=CN))+ geom_boxplot()+geom_text(data=Valuemax_lsd_CN, aes(x=Trt, y=0.1+max_value, label=SigLetter_CN$groups),position = position_dodge(width = 0.9),vjust = -(0.5))+theme(plot.title = element_text(hjust = 0.5),legend.position="bottom")+ ylab("C:N ratio \n 2022")+ xlab("Treatment")

```

# The parameters correlation on Pearson test 

```{r cor, echo=FALSE}
Y= stb_tom %>% 
 select(7:25)%>% 
  select(-dgtx,-Graminoid_CR,-soiltx)

res2 <- rcorr(as.matrix(Y))
#extarct r &p
correlation_r = res2$r
correlation_p = res2$P

Corrlation_test1=flattenCorrMatrix(res2$r, res2$P)%>%
  filter(p<=0.05,cor<=-0.5)
Corrlation_test2=flattenCorrMatrix(res2$r, res2$P)%>%
  filter(p<=0.05,cor>=0.5)

#Select p<=0.05,cor>=0.5 or cor<=-0.5
Correlation=rbind(Corrlation_test1,Corrlation_test2)

print(Correlation)
```

# The normal distribution changes of Soil stability in 2023

```{r normality_stb, echo=FALSE}
changes <- read_csv("Parameters_changes.csv")

changes$Block=as.factor(changes$Block)
changes$Trt=as.factor(changes$Trt)

list_changes_t=which(changes$Trt=="T_Viti")
changes_t=changes[list_changes_t,]


list_changes_A=which(changes$Trt=="A_Viti")
changes_A=changes[list_changes_A,]



list_changes_D=which(changes$Trt=="D_Viti")
changes_D=changes[list_changes_D,]


chgs_stb= lm(Stability~Trt+Block, data=changes)
anova(chgs_stb)
lsd.chg.trt=LSD.test(chgs_stb,"Trt")
lsd.chg.trt

s1=ggdensity(changes_t, x = "Stability", fill = "lightgray", title = "T_Viti\n                 b")  + ylab("Number of Data Points")+ xlab("The changes of Soil Stability (MWD)\n 2019 to 2023") + xlim(-0.5,2) + ylim(0,2)
s2=ggdensity(changes_A, x = "Stability", fill = "lightgray", title = "A_Viti\n                 a") + ylab("Number of Data Points")+ xlab("The changes of Soil Stability (MWD)\n 2019 to 2023") + xlim(-0.5,2) + ylim(0,2)
s3=ggdensity(changes_D, x = "Stability", fill = "lightgray", title = "A_Viti\n                 a")  + ylab("Number of Data Points")+ xlab("The changes of Soil Stability (MWD)\n 2019 to 2023")+ xlim(-0.5,2) + ylim(0,2)

plot_grid(
  s1,s2,s3,
  nrow=1,ncol=3
)
```


# The normal distribution changes of total soil organic matter in 2022
```{r normality_TOM, echo=FALSE}

chgs_TOM= lm(TOM~Trt+Block, data=changes)
anova(chgs_TOM)
lsd.chg.TOM=LSD.test(chgs_TOM,"Trt")
lsd.chg.TOM

C1=ggdensity(changes_t, x = "TOM", fill = "lightgray", title = "T_Viti\n                 b")  + ylab("Number of Data Points")+ xlab("The changes of total organic matter \n 2021 to 2022")+xlim(-1,2)+ylim(0,4)
C2=ggdensity(changes_A, x = "TOM", fill = "lightgray", title = "A_Viti\n                 a") + ylab("Number of Data Points")+ xlab("The changes of total organic matter \n 2021 to 2022")+xlim(-1,2)+ylim(0,4) 
C3=ggdensity(changes_D, x = "TOM", fill = "lightgray", title = "A_Viti\n                 a") + ylab("Number of Data Points")+ xlab("The changes of total organic matter \n 2021 to 2022")+xlim(-1,2)+ylim(0,4)

plot_grid(
  C1,C2,C3,
  nrow=1,ncol=3
)
```


# The changes of parameters (After-before)
```{r cor_change, echo=FALSE}
Y= changes %>% 
 select(4:13)

res <- rcorr(as.matrix(Y))
#extarct r &p
r = res$r
p = res$P

test1=flattenCorrMatrix(res$r, res$P)%>%
  filter(p<=0.05,cor<=-0.5)
test2=flattenCorrMatrix(res$r, res$P)%>%
  filter(p<=0.05,cor>=0.5)

#Select p<=0.05,cor>=0.5 or cor<=-0.5
Cor_Change=rbind(test1,test2)%>%
  arrange(cor)
  
print(Cor_Change)
```

# The cover crop coverage 
- obs: 2 trts (Aviti + Dviti) x 2 years x 4 cover crop categories

```{r covercrop, echo=FALSE}
covercrop <- read_csv("covercrop.csv")

ggplot(data=covercrop, aes(x=covercrop, y=CoverRate, fill=Treatment)) +
  geom_bar(stat="identity", position=position_dodge())+ylab("Cover Rate (%)")+ xlab("Cover crop")+
theme(plot.title = element_text(hjust =0.5),legend.position="bottom")+ theme(
axis.title.x = element_text(size=14),
axis.title.y = element_text(size=14))
```

